Supermarket ouptut

### 2021-01-24 reports/supermarket-output.Rmd
Updates graphs with proper axes

### Effect of session on maximum achieved difficulty
```{r}
df_results_remediation %>%
  group_by(session, participant) %>%
  summarise(n_trials = max(n_trials), .groups="drop") %>%
  ggplot(aes(session, y = n_trials, color = participant)) +
    geom_point()+
    geom_smooth(method = "lm", se = FALSE) + 
    facet_wrap(~participant) +
    guides(color = FALSE) +
    scale_x_continuous(breaks = 2:12) +
    labs(y = "Maximum achieved difficulty")
```

```{r}
df_results_remediation %>%
  group_by(session, participant) %>%
  summarise(n_trials = max(n_trials)) %>%
  ggplot(aes(session, n_trials)) +
    geom_jitter(aes(color=participant), height = 0.1, width = 0.2) +
    geom_smooth(method = "lm") +
    scale_x_continuous(breaks = 2:12) +
    scale_y_continuous(breaks = 1:15) +
    labs(y="maximum achieved difficulty") + guides(color=FALSE)
```

```{r}
df_results_remediation %>%
  group_by(session, participant) %>%
  summarize(max_difficulty = max(n_items), .groups = "drop") %>%
  lmer(max_difficulty ~ session  + (session||participant), data = .) %>%
    VarCorr()
```

>>>>

### Effect of session on maximum achieved difficulty
```{r}
df_results_remediation %>%
  group_by(session, participant) %>%
  summarise(max_difficulty = max(n_items), .groups="drop") %>%
  ggplot(aes(session, y = max_difficulty, color = participant)) +
    geom_point()+
    geom_smooth(method = "lm") + 
    facet_wrap(~participant) +
    guides(color = FALSE) +
    scale_x_continuous(breaks = 2:12) +
    labs(y = "Maximum achieved difficulty")
```

```{r}
df_results_remediation %>%
  group_by(session, participant) %>%
  summarise(max_difficulty = max(n_items)) %>%
  ggplot(aes(session, max_difficulty)) +
    geom_jitter(aes(color=participant), height = 0.1, width = 0.2) +
    geom_smooth(method = "lm") +
    scale_x_continuous(breaks = 2:12) +
    scale_y_continuous(breaks = 1:15) +
    labs(y="maximum achieved difficulty") + guides(color=FALSE)
```

```{r}
df_results_remediation %>%
  group_by(session, participant) %>%
  summarize(max_difficulty = max(n_items), .groups = "drop") %>%
  lmer(max_difficulty ~ session  + (session|participant), data = .) %>%
    VarCorr()
```
